---
title: Regression Models
author: R package build
date: '2022-03-26'
slug: regression-models
categories: []
tags: []
---

## Libraries
```{r}
library(tidyverse)
library(ISLR)
library(boot)
library(readxl)
```

#Get Data
```{r}
df <- read_excel("data/Professor_Proposes_Data.xlsx")
df$Price <- as.numeric(df$Price)
df$Wholesaler <- as.factor(df$Wholesaler)
```

```{r}
#Set seed
set.seed(1)
head(df)
dim(df)
#Index
train <- sample(440,220)
head(train)
```


```{r}
# focus on Wholesaler 1 and 2 rather than Wholesaler 3
dfw <- df %>%
    filter(Wholesaler == 3)

max(dfw$Carat)
```
# Data 

```{r}
qplot(df$Price, geom="histogram",fill = "Orange", xlab = "Price", main = "Price of diamond", ylab = "Frequency") 
```

```{r}
qplot(df$Carat, geom="histogram",fill = "Orange", xlab = "Carat", main = "Carat", ylab = "Frequency") 
```

# Data Tables
Clarity
```{r}
table(df$Clarity)
```

Color
```{r}
table(df$Colour)
```

Cut
```{r}
table(df$Cut)
```

Certification
```{r}
table(df$Certification)
```

Polish
```{r}
table(df$Polish)
```

Symmetry
```{r}
table(df$Symmetry)
```

# ANOVA

Carat
```{r}
one.way <- aov(Price ~ Carat, data = df)

summary(one.way)
```

Clarity
```{r}
one.way <- aov(Price ~ Clarity, data = df)

summary(one.way)
```

Certification
```{r}
one.way <- aov(Price ~ Certification, data = df)

summary(one.way)
```

Cut
```{r}
one.way <- aov(Price ~ Cut, data = df)

summary(one.way)
```

Polish
```{r}
one.way <- aov(Price ~ Polish, data = df)

summary(one.way)
```

Symmetry
```{r}
one.way <- aov(Price ~ Symmetry, data = df)

summary(one.way)
```

Color
```{r}
one.way <- aov(Price ~ Colour, data = df)

summary(one.way)
```


# Graph
```{r}
df %>%
    ggplot(aes(x=Carat, y = Price, color = Wholesaler)) +
        geom_point()      
```



```{r}
dfw23 <- df %>%
  filter(Wholesaler == 2 | Wholesaler == 1)

dim(dfw23)

dfw23 %>% 
  ggplot(aes(x = Carat, y = Price, color = Wholesaler 
    )) +
  geom_point()
attach(dfw23)
```


# Boot Function

```{r}
# Dimension of new data frame
dim(dfw23)
```

```{r}
boot.fn <- function(data, index) {
  return(coef(lm(Price~Carat + Colour + Clarity+ Cut + Certification + Polish + Symmetry, data = data , subset = index)))
}
set.seed(1)
boot.fn(dfw23, sample(240, 240, replace=T))
```

# Answer
The price that the professor found is $3100 for a specific diamond. I looked at the data and added up all of the coefficients to get the price from my calculations. The price that I found equals to 2,844 dollars which is 300 dollars off the original value. If the intercept value was not included than the predicted value would be 3,132 dollars.










